The Real-time fMRI Neurofeedback Based Stratification of Default Network Regulation Neuroimaging Data Repository.

### 2016-10-08 mcdonald_nfb_datasharing_body.tex
minor formatting fixes

\subsection{Phenotypic data}
Basic phenotypic data, which includes age, sex and handedness are available in the \textt{participants.tsv} file at the root of the repository. Comprehensive phenotypic data are available as comma separated value (.csv) files from COINS after completing a minimal data usage agreement. Summary scores calculated from the RVIP task info area available through COINs and trial-by-trial response information is available via NITRC (Data Citation Y1: \url{http://fcon\_1000.projects.nitrc.org/indi/enhanced/RVIP-master.zip}).

@@

For the MSIT, fMRI data should be analyzed as 42s blocks with the following onset times after dropping the first four TRs: congruent blocks - 22, 106, 190, 274; incongruent blocks –64,148, 232, 316. The Moral Dilemma fMRI data should be analyzed as 30s blocks with the following onset times after dropping the first four TRs: control blocks – 12, 72, 132, 192; dilemma blocks – 42, 102, 162, 222. Note that up until April 2014 (first 11 participants), no pre-experiment fixation period was implemented for the moral dilemma task. For those participants, all of the aforementioned stimulus onset times should be altered by subtracting 20s. For analysis of the NFB fMRI data, the first stimulus onset (and duration) times, in seconds, are as follows: 34(30), 162(60), 260(90), 418(60), 576(30), 674(90). The second stimulus onset (and duration) times, in seconds, are as follows: 68(90), 226(30), 354(60), 482(90), 610(60), 768(30). This timing information is also available in \textttt{events.tsv} files provided in the repository alongside the task fMRI data.

>>>>

\subsection{Phenotypic data}
Basic phenotypic data, which includes age, sex and handedness are available in the \texttt{participants.tsv} file at the root of the repository. Comprehensive phenotypic data are available as comma separated value (.csv) files from COINS after completing a minimal data usage agreement. Summary scores calculated from the RVIP task info area available through COINs and trial-by-trial response information is available via NITRC (Data Citation Y1: \url{http://fcon\_1000.projects.nitrc.org/indi/enhanced/RVIP-master.zip}).

@@

For the MSIT, fMRI data should be analyzed as 42s blocks with the following onset times after dropping the first four TRs: congruent blocks - 22, 106, 190, 274; incongruent blocks –64,148, 232, 316. The Moral Dilemma fMRI data should be analyzed as 30s blocks with the following onset times after dropping the first four TRs: control blocks – 12, 72, 132, 192; dilemma blocks – 42, 102, 162, 222. Note that up until April 2014 (first 11 participants), no pre-experiment fixation period was implemented for the moral dilemma task. For those participants, all of the aforementioned stimulus onset times should be altered by subtracting 20s. For analysis of the NFB fMRI data, the first stimulus onset (and duration) times, in seconds, are as follows: 34(30), 162(60), 260(90), 418(60), 576(30), 674(90). The second stimulus onset (and duration) times, in seconds, are as follows: 68(90), 226(30), 354(60), 482(90), 610(60), 768(30). This timing information is also available in \texttt{events.tsv} files provided in the repository alongside the task fMRI data.
